\sysfull

### 2017-08-11 paper/evaluation.tex
work on evaluation

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{l|cc|cc|cc|cc|c}
		\hline
		{} & \multicolumn{2}{l|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for dd, dft, sort missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

@@

\subsubsection{\sys Coalescing Overhead}
\label{sec:result_compiler_time}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{\sys coalescing overhead measured per application.}
	\label{fig:coalescing}
\end{figure}

Result is provided in Figure~\ref{fig:coalescing}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average virtual task size.}
	\label{fig:aveVirtuTaskSize}
\end{figure}

Measured size of tasks for each application is given in Figure~\ref{fig:aveVirtuTaskSize}.

>>>>

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{|l|cc|cc|cc|cc|c|}
		\hline\hline
		{} & \multicolumn{2}{l|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for dd, dft, sort missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

@@

\subsubsection{\sys Coalescing Performance}
\label{sec:result_compiler_time}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{\sys coalescing performance measured per application at fixed power and various WISP to RFID antenna distances, \{20, 40, 60\}\,cm, assessed against non-coalescing \sys.}
	\label{fig:coalescing}
\end{figure}

We measured \sys coalescing performance. Result is provided in Figure~\ref{fig:coalescing}. Result clearly show that coalescing provides a benefit for all applications, providing even seven times improvement for bc application at 40\,cm.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average \sys virtual task size at fixed power per application. Top (green): number of coalesced tasks; bottom (red): average size of real task.}
	\label{fig:aveVirtuTaskSize}
\end{figure}

We need to know how many tasks \sys can coalesce. We ran a subset of applications (split by tasks manually) with continuous power supply and measured the size of tasks for each application and amount of tasks coalesced. Result is given in Figure~\ref{fig:aveVirtuTaskSize}. We see clearly that \sys manages to coalesce more tasks as individual tasks are small. As the size of individual task increases, e.g., as in the case of dft application, the number of coalesced tasks is also small. This result clearly shows that for the benefit of coalescing and for code portability, initial code should be split by \emph{as small tasks as possible}.
